An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-12-31 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Changed to using oModels in the code we don't use.

<<abg_trajectories, eval=FALSE>>=
# This code can be run to test the conclusion about the LINEX model meeting constraints.
# This chunk of R code has eval=FALSE, because it is not a part of the paper.
Calvin_Models <- loadPostProcessedData(Source = "Calvin", kind = "models", dir=pp_path)
abgplotdata <- fortify(Calvin_Models$Calvin$IR$linex$`iK+iL+iQp`)
triPlot(data=abgplotdata, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
@

>>>>

<<abg_trajectories, eval=FALSE>>=
# This code can be run to test the conclusion about the LINEX model meeting constraints.
# Need to put oModels in the environment much earlier in this file.
# This chunk of R code has eval=FALSE, because it is not a part of the paper.
abgplotdata <- fortify(oModels$Calvin$IR$linex$`iK+iL+iQp`)
triPlot(data=abgplotdata, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear")
@
